---
title: Bayesian A/B Testing 
format: gfm
---

> Source: Hoffmann, T., Hofman, A. D., & Wagenmakers, E. (2021, June 10). A Tutorial on Bayesian Inference for the A/B Test with R and JASP. https://doi.org/10.31234/osf.io/z64th


There are two approaches to Bayesian A/B testing.

1. Independent Beta Estimation (IBE) Approach

2. The Logit Transformation Testing (LTT) Approach


## Independent Beta Estimation (IBE) Approach

**Problem Statement:** We want to know whether honey bees have color vision.

**Experiment Design:** The experiment involves a training and a testing phase. 
In the training phase, the bees in the experimental condition are presented with 
a blue and a green disc. Only the blue disc is covered with a sugar lotion that 
bees crave. The control group receives no training. In the testing phase, the 
sugar lotion is removed from the blue disc, and the behavior of both groups is 
being observed. If the bees in the experimental condition have learned that only
the blue disc contains the appetising sugar lotion, and if they can discriminate 
between blue and green, they should preferentially explore the blue instead of 
the green disc during the testing phase.

**Treatment Arms:** A: Treatment (i.e. received training), B: Control (No training).

**Priors:** Two uninformative uniform priors, i.e. Beta(1, 1).

```{r}
#| label: ab1-setup
#| message: false
library(dplyr)
library(bayesAB)
library(HDInterval)
```


```{r}
bees_01_df <- read.csv(here::here("data/bees_data1.csv"), sep = ";") %>% 
  select(bees_id = X, y1, y2)

head(bees_01_df)
```

```{r}
ab1 <- bayesTest(
  A_data = bees_01_df$y2, # new intervention
  B_data = bees_01_df$y1, # existing intervention
  priors = c('alpha' = 1, 'beta' = 1),
  n_samples = 1e+05,
  distribution = "bernoulli"
)
```


```{r}
ab_sum <- summary(ab1)

ab_sum
```


The following figure presents the independent posterior beta distribution of the success
probabilities for the group A & B.

```{r}
plot(ab1)$posteriors
```

We can see that the group A's posterior distribution assigns more mass to higher values
of $\theta$. This suggest that the trained bees has higher success probability, which in 
turn implies that bees have color vision.


The following figure presents the conversion rate uplift from version B (control) to
version A (treatment).

```{r}
plot(ab1)$samples
```


The posterior distribution for the uplifts peaks at ~0.28, which means most likely
uplift will be 28%. And 98.4% posterior samples are above zero. 


```{r}
ab_sum$probability
```

$P(A > B \; \vert \; Data) = 0.984$.

That is, we can be 98.4% certain that group A approaches the blue disc more often
than the group B. Putting it generically, we can be 98.4% certain group A has better 
success rate than group B.

**Note that, by assuming $Beta(1, 1)$ prior, i.e. uniform prior before
seeing any data, we are assuming that the both positive and negative treatment effect
are equally likely.**




